Article Title

### 2013-10-03 plos.tex
minor
added Figure1.pdf
ongoing changes in the Results section
minor edits
worked on the description of estimators.
updated estimator descriptions.
completed estimator description.
redistributed text between files, cleaned up text files.
put all figures and sections in place.
clarified "Evaluation of estimators" based on Kreso's input.
math corrections in Estimators.tex

\DeclareMathOperator{\Tr}{tr}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\T}{\intercal}
\newcommand{\TODO}[1]{\emph{\small\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander Ecker$^{3,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
\bf{3} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

@@

% Results and Discussion can be combined.
\section*{Results}
\input{sections/Results.tex}

\section*{Discussion}
%\input{sections/Discussion.tex}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figures/Figure1.pdf}
\end{center}
\caption{
{\bf Acquistion of neural population activity using two-photon fluorescence imaging of calcium signal.}  {\tt A.} Visual stimuli comprising full-field  
}
\label{Figure_label}
\end{figure}

>>>>

\DeclareMathOperator{\Tr}{tr}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\mcond}{\,\middle\vert\,}
\newcommand{\cond}{\,\vert\,}
\newcommand{\loss}[1]{\mathcal L\left(#1\right)} 
\newcommand{\T}{\intercal}
\newcommand{\E}[2][]{\mathbb E_{#1}\left[ #2\right]}    % expected value
\newcommand{\TODO}[1]{\emph{\small\color{blue}$\langle\langle$#1$\rangle\rangle$}}
\newcommand*\dif{\mathop{}\,d}
\DeclareMathOperator{\rank}{rank}

@@

% Title must be 150 characters or less
\begin{flushleft}
{\Large
Improved estimates of neural correlations suggest detailed interactions in visual cortex
}
% Insert Author names, affiliations and corresponding author email.
\\
Dimitri Yatsenko$^{1,\ast}$, 
Kre\v{s}imir Josi\'{c}$^{2}$,
Alexander Ecker$^{3,1}$,
Emmanouil Foudarakis$^{1}$,
R.~James Cotton$^{1}$,
Andreas S.~Tolias$^{1}$
\\
\bf{1} Department of Neuroscience, Baylor College of Medicine, Houston, TX, USA
\\
\bf{2} Department of Mathematics and Department of Biology and Biochemistry, University of Houston, Houston, TX, USA
\\
\bf{3} Max Planck Institute of Biological Cybernetics, T\"ubingen, Germany
\\
$\ast$ E-mail: yatsenko@cns.bcm.edu
\end{flushleft}

@@

% Results and Discussion can be combined.
\section*{Results}
\input{sections/Acquisition.tex}
\input{sections/Theory.tex}
\input{sections/Regularization.tex}
\input{sections/Estimators.tex}
\input{sections/Simulation.tex}
\input{sections/Findings.tex}
\input{sections/Structure.tex}

\section*{Discussion}
\input{sections/Discussion.tex}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\input{sections/Methods.tex}

@@

\section*{Figure Legends}
\TODO{presently embedded in the text}

### 2013-10-03 sections/Theory.tex
minor

For the purposes of this study, we adopted the \emph{negative normal log-likelihood loss} function:
\begin{equation}\label{eq:loss}
\loss{\hat\Sigma,\Sigma} = \frac 1 p\left[\ln \det \hat \Sigma + \Tr(\hat \Sigma^{-1}\Sigma)\right]
\end{equation}
This choice is motivated by mathematical convenience. Other popular choices for the loss function are the Frobenius norm of the difference $\hat\Sigma-\Sigma$, Stein's entropy loss, and quadratic loss \cite{James:1961,Ledoit:2004,Schafer:2005,Fan:2008}.  We expect that the main conclusions of our study will not change qualitatively under other well behaved loss functions.

>>>>

For the purposes of this study, we adopted the \emph{negative normal log-likelihood loss} function:
\begin{equation}\label{eq:loss}
\loss{\hat\Sigma,\Sigma} = \frac 1 p\left[\ln \det \hat \Sigma + \Tr(\hat \Sigma^{-1}\Sigma)\right]
\end{equation}
This choice is motivated by mathematical convenience. Other popular choices for the loss function are the Frobenius norm of the difference $\hat\Sigma-\Sigma$ \cite{Ledoit:2004,Schafer:2005}, Stein's entropy loss, and quadratic loss \cite{James:1961,Fan:2008}.  We expect that the main conclusions of our study will not change qualitatively under other well behaved loss functions.
